Racial and Ethnic Differences in ETI: Outcomes

### 2024-07-22 Kamyron Jordan/Racial and Ethnic Differences in ETI/racial_and_ethnic_differences_in_eti_outcomes.qmd
parallelize ETI outcomes

```{r setup}
#| include: false
# Libraries
library(tidyverse)
library(lmerTest)
library(splines)
library(ggeffects)
library(gtsummary)
library(ggflowchart)
# Paths
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF",
  "Windows" = "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF",
  "Linux" = "/home/timvigers/OneDrive/Vigers/CF"
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

```{r results='asis'}
#| warning: false
invisible(lapply(continuous_outcomes, function(o) {
  cat("\n")
  cat("\n")
  cat("##", o)
  cat("\n")
  cat("\n")
  print(loess_plot(outcome = o))
}))
```

@@

```{r}
invisible(lapply(continuous_outcomes, function(o) {
  f <- as.formula(paste0(
    o,
    "~ age_group + Insurance + bs(Days, knots = 0, degree = 1) * Race + (1 | eDWID)"
  ))
  m <- lmer(f, data = encounter %>% filter(Race != "Asian"))
  predict_response(model = m, terms = c("Days[all]", "Race")) %>%
    plot() %>%
    print()
}))
```

>>>>

```{r setup}
#| include: false
# Libraries
library(tidyverse)
library(lmerTest)
library(splines)
library(ggeffects)
library(gtsummary)
library(ggflowchart)
library(parallel)
# Paths
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF",
  "Windows" = "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF",
  "Linux" = "/home/timvigers/OneDrive/Vigers/CF"
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

```{r}
cl <- makeForkCluster(detectCores() / 2)
invisible(parLapply(cl, continuous_outcomes, function(o) {
  cat("\n")
  cat("\n")
  cat("##", o)
  cat("\n")
  cat("\n")
  print(loess_plot(outcome = o))
}))
```

@@

```{r}
invisible(parLapply(cl, continuous_outcomes, function(o) {
  f <- as.formula(paste0(
    o,
    "~ age_group + Insurance + bs(Days, knots = 0, degree = 1) * Race + (1 | eDWID)"
  ))
  m <- lmer(f, data = encounter %>% filter(Race != "Asian"))
  predict_response(model = m, terms = c("Days[all]", "Race")) %>%
    plot() %>%
    print()
}))
stopCluster(cl)
```
